Hypertension and microbiome

### 2019-02-27 articletwo.Rmd
Minor
Core

@@

maaslin$genus <- maaslinwrapper(pseq = pseq.genus,
                looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION"),
                forced = c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03",
                           "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                taxa = "Halapricum.Archaea-")

lactotaxa <- paste0(c("Lactobacillus_delbrueckii.Bacteria", "Lactobacillus_ruminis.Bacteria", "Lactobacillus_acidophilus.Bacteria",
                    "Lactobacillus_fermentum.Bacteria", "Lactobacillus_paracasei.Bacteria", "Lactobacillus_salivarius.Bacteria"), collapse = ",")

maaslin$lacto.min <- maaslinwrapper(pseq = (subset_taxa(pseq.species, Genus=="Lactobacillus")),
                looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION"),
                forced = c("BL_AGE", "SEX"),
                taxa = lactotaxa)

maaslin$lacto.max  <- maaslinwrapper(pseq = (subset_taxa(pseq.species, Genus=="Lactobacillus")),
                looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION"),
                forced =c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03",
                          "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                taxa = lactotaxa)
```

@@

```{r save session}
save.session(paste0("cache/session-", now, ".Rda"))
```

>>>>

```{r core taxa}
pseq.genus.core <- core(pseq.genus, detection = 0.001, prevalence = 0.01)
pseq.species.lactobacillus <- subset_taxa(pseq.species, Genus=="Lactobacillus")
pseq.species.lactobacillus.core <- core(pseq.species.lactobacillus, detection = 0.001, prevalence = 0.01)
```

At genus level core has number of taxa `r ntaxa(pseq.genus.core)` (`r
ntaxa(pseq.genus)`). For lactobacilli core has number of taxa `r
ntaxa(pseq.species.lactobacillus.core)` (`r ntaxa(pseq.species.lactobacillus)`).

@@

maaslin$genus <- maaslinwrapper(pseq = pseq.genus.core,
                looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION"),
                forced = c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03",
                           "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                taxa = "Halapricum.Archaea-")

lactotaxa <-c("Lactobacillus_delbrueckii.Bacteria", "Lactobacillus_ruminis.Bacteria", "Lactobacillus_acidophilus.Bacteria",
                    "Lactobacillus_fermentum.Bacteria", "Lactobacillus_paracasei.Bacteria", "Lactobacillus_salivarius.Bacteria")

maaslin$lacto.min <- maaslinwrapper(pseq = pseq.species.lactobacillus.core,
                looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION"),
                forced = c("BL_AGE", "SEX"),
                taxa =  paste0(lactotaxa,  collapse = ","))

maaslin$lacto.max  <- maaslinwrapper(pseq = pseq.species.lactobacillus.core,
                looped = c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION"),
                forced =c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB", "BL_USE_RX_C03",
                          "BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09"),
                taxa = paste0(lactotaxa collapse = ","))
```

@@

```{r save session}
save.image(file = paste0("cache/session-", now, ".Rdata"))
```
